Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-05-05 SIR_manuscript.tex
analysis, R0 wrt rho

The Disease-Free Equilibrium (DFE) for the SIR model, Eqs. \eqref{model}, is found by setting the infected compartments to 0 and solving for the unknowns. The DFE is
\begin{equation}
\label{dfe}
S\_n^*= \frac{\rho}{\omega} N_0, \ S\_u^*= N_0-S\_n^*, \text{~and~} I_j=R_j=0 \ \text{for all }j.
\end{equation}
The corresponding \percap testing rate (Eq. \ref{F}) for the infected compartment $I$ at DFE is one of the key analysis parameters and can be simplified as 
\begin{equation}
\label{eq:fi}
\hat F_I = (\omega\rho/(\omega-\rho))w_I/w_S.
\end{equation}

@@

where parameters are specified in Table \ref{tab:params}. The next generation matrix for this model is $G = F V^{-1}$, where matrix $F$ represents the inflow of new infection to the infected compartments and matrix $V$ represents the flow in the infected compartments when the population is totally susceptible. 
Matrices $F$ and $V$ are
\begin{align}
\label{FV}
F =& \beta/N_0 \left[ \begin {array}{cccc} 
S\_u^* & (1-\theta\_w)\,S\_u^* & (1-\theta\_w)\,S\_u^* & (1-\theta\_c)\,S\_u^*\\
(1-\theta\_w)S\_n^* & (1-\theta\_w)^2\,S\_n^* & (1-\theta\_w)^2\,S\_n^* & (1-\theta\_w)(1-\theta\_c)\,S\_n^* \\ 
0&0&0&0\\
0&0&0&0
 \end {array} \right] \\
 =&\beta/N_0 \left[ \begin {array}{c} S\_u^* \\ (1-\theta\_w)S\_n^* \\ 0 \\ 0 \end {array} \right]
        \left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right], \text{and}\\  V=&
 \left[ \begin {array}{cccc}  
\hat F_I+\gamma&-\omega&0&0\\
-(1-p_I)\hat F_I&\omega+\gamma&0&0\\
-p_I \hat F_I&0&\omega+\gamma&0\\
0&0&-\omega&\gamma
\end {array} \right].
\end{align}
The matrix inverse of $V$ is 
\begin{align}
\label{vinv}
V^{-1} =&
\frac{1}{\gamma C}
\left[ \begin {array}{cccc}
\gamma(\omega+\gamma)^2 & \gamma\omega(\omega+\gamma)&0&0\\ \noalign{\medskip}
\gamma(\omega+\gamma)(1-p_I) \hat F_I & \gamma(\omega+\gamma)(\hat F_I+\gamma)&0&0 \\ \noalign{\medskip}
\gamma(\omega+\gamma) p_I \hat F_I & \gamma\omega p_I \hat F_I & C \gamma/(\omega+\gamma) & 0 \\ \noalign{\medskip}
\omega(\omega+\gamma) p_I \hat F_I & \omega^2 p_I \hat F_I & C \omega/(\omega+\gamma) & C
\end {array} \right],
\end{align}
where $C= \big( \gamma(\omega+\gamma)+(\gamma+\omega p_I)\hat F_I \big) (\omega+\gamma)$ and $\hat F_I$ is the \percap testing rate for the infected people and represented in Eq. \eqref{eq:fi}. Note that all the columns of matrix $V^{-1}$ summ up to $1/\gamma$.

@@

This is to provide a mathematical materials to prove that $\pro \Delta$ can be positive or negative, with $\Delta$ defined in Eq. \eqref{eq:abc}, and thus $\pro \Rnum < 0$, where $\Rnum$ is the basic reproduction number, given in Eqs.\,\eqref{R0}. We can rewrite matrix $G_{11}$ in \eqref{G11} in the following form to simplify the calculations.
\begin{equation}
\label{G112}
G_{11} = \frac{\beta}{\gamma \, C} 
\left[ \begin {array}{c}  (\omega-\rho)/\omega \\ (1-\theta\_w)\rho/\omega  \end {array} \right]
\left[ \begin {array}{cccc} 
C-C_1, C-C_1-C_2\end {array} \right],
\end{equation}
where $C$ is the same as the one in Eq. \eqref{eq:abc}, i.e., 
$$C=(\omega+\gamma)(\gamma(\omega+\gamma)+(\omega\,p_I+\gamma)\,\hat F_I),$$
and $C_1$ and $C_2$ are 
\begin{align}
\label{eq:C12}
C_1 =& (\omega+\gamma)(\theta\_w \, \gamma+\theta\_c\, \omega\, p_I) \hat F_I,\\
C_2 =& (\omega+\gamma)\gamma^2\,\theta\_w+(\theta\_w-\theta\_c)\gamma\,\omega\,p_I\,\hat F_I,
\end{align}
where $\hat F_I$ is given in Eq. \eqref{eq:fi}.
$\Rnum$ is in the same form as in Eq. \eqref{R0}  
$$\Rnum= \frac{\beta}{\gamma} (1-\Delta),$$
where 
\begin{equation}
\label{eq:del4}
\Delta= \frac{1}{N_0\,C}\big(C_1\,S\_u^*+((C_1+C_2)(1-\theta\_w)+C\,\theta\_w)\,S\_n^*\big).
\end{equation}
Note that for analysis convention, we let $N_0=1$, thus $S\_u^*$ and $S\_n^*$ are in the scale of 0 to 1. 
To derive the first result, i.e., how changes in $\theta\_w$ and $\theta\_c$ affects $\Rnum$, we factor these parameters in $\Delta$ \eqref{eq:del4}. Thus, $\Delta$ can be rewritten as
\begin{equation}
\label{eq:del4_theta}
\Delta= \frac{1}{C}\Big(
-D_1\,S\_n^*\,\boldsymbol {\theta\_w^2}+
\big(-\omega^2\,p_I\,\hat F_I\,S\_n^*\,\boldsymbol{\theta\_c}\,+\,D_2\,S\_n^*\,+\,\gamma\,\hat F_I(\omega+\gamma) \big)\boldsymbol{\theta\_w}+
(\omega+\gamma\,S\_u^*)\omega\,p_I\,\hat F_I\,\boldsymbol{\theta\_c}
\Big),
\end{equation}
where
\begin{align}
\label{eq:del4_d1d2}
D_1=& (\omega+\gamma)\gamma^2+(\omega+\gamma+\omega\,p_I)\gamma\,\hat F_I, \\
D_2=& (3\omega+2\gamma)\gamma^2+(\omega+\gamma+2\omega\,p_I)\gamma\,\hat F_I+(\gamma+p_I\,\hat F_I)\omega^2.
\end{align}
The scaled expression of $\Delta$, specifically $\Delta\,C$, in Eq.\,\eqref{eq:del4_theta} is linear in $\theta\_c$ with a positive coefficient given by 
$$(\gamma\,S\_u^*\,+\omega(1-\theta\_w\,S\_u^*))\omega\,p_I\,\hat F_I.$$
This results in increasing $\Delta$, thus decreasing $\Rnum$ with respect to $\theta\_c$, that is $\pder[\Rnum]{\theta\_c}\leq 0$. Note that $C$ is independant of $\theta\_c$ and $\theta\_w$.

With a similar logic, the expression of $\Delta\,C$ derived from Eq.\,\eqref{eq:del4_theta} is a concave-down quadratic equation in $\theta\_w$, given by
\begin{equation}
\label{eq:del4_thetaw}
-D_1\,S\_n^*\,\boldsymbol {\theta\_w^2}+
\big(-\omega^2\,p_I\,\hat F_I\,S\_n^*\,\boldsymbol{\theta\_c}\,+\,D_2\,S\_n^*\,+\,\gamma\,\hat F_I(\omega+\gamma) \big)\boldsymbol{\theta\_w}.
\end{equation}
We show that the feasible range of $\theta\_w$ lies btween 0 and the vertex of this parabola where the parabola is increasing in $\theta\_w$, and so does $\Delta$ which results in inferring $\pder[\Rnum]{\theta\_w}\leq 0$.
It is enough to show that partial derivative of the expression \eqref{eq:del4_thetaw} with respect to $\theta\_w$ at $\theta\_w=1$ is non-negative. It follows that
\begin{align}
\label{eq:d_del4_thetaw}
\pder[\Delta\,C]{\theta\_w}\bigg\rvert_{\theta\_w=1} =&
(D_2-2D_1-\omega^2\,p_I\,\hat F_I\,\theta\_c)\,S\_n^*+\gamma\,\hat F_I(\omega+\gamma) \\
=& (\gamma(\omega+\gamma)+\gamma\omega^2+(1-\theta\_c)\omega^2\,p_I\,\hat F_I )\,S\_n^*
+\gamma(\omega+\gamma)\,\hat F_I\,(1-S\_n^*),
\end{align}
which is a positive quantity, given that $\theta\_c$ and $S\_n^*$ vary between 0 and 1.

\ali{stoped here!}

Let define $\phi = \hat F_S = \frac{\rho \omega}{\omega-\rho}$, thus
\begin{equation}
\label{eq:phi}
\rho=\frac{\omega \phi}{\omega+\phi}.
\end{equation}
Reparametrizing testing rate $\rho$ by $\phi$ in the expression of $\Rnum$, in Eq.\,\eqref{R0}, and applying the derivative with respect to $\phi$ results in the following simplified expression for $\partial\Delta/\partial\phi$.

with an equivalent but simplified $\Delta$ in Eq.\,\eqref{eq:abc} as
\begin{equation}
\label{eq:del3}
\Delta= \frac{K_1\,\phi^2+K_2\,\phi}{K_3},
\end{equation}
where
\begin{align}
\label{eq:K}
K_1=& \frac{w_I}{w_S}\Big(((1+p_I)\omega+\gamma)\gamma\theta\_w+\omega^2 p_I\theta\_c \Big), \\
K_2=& (\omega+\gamma)\Big( (\frac{w_I}{w_S}\omega+\gamma)\gamma\theta\_w + \frac{w_I}{w_S} \omega^2 p_I\theta\_c \Big),\\
K_3=& (\omega+\gamma) \Big((\omega p_I+\gamma)\frac{w_I}{w_S}\phi\,+\,(\omega+\gamma)\gamma \Big)(\omega+\phi).
\end{align}
The derivative is
\begin{align}
\label{eq:dd3dr}
\partial\Delta/\partial\phi=& \frac{1}{d_3} (a_3\,\phi^2+b_3\,\phi+c_3),
\end{align}
where
\begin{align}
\label{eq:abcd2}
a_3=& \frac{w_I}{w_S} \Big((\omega\,p_I+\gamma)(\theta\_w-\theta\_c)\frac{w_I}{w_S}\omega\,p_I+(\gamma\theta\_w+\omega\,p_I\theta\_c)(\omega+\gamma) \Big),\\
b_3=& 2\frac{w_I}{w_S}(\omega+\gamma)\Big( ((1+p_I)\omega+\gamma)\gamma\theta\_w+\omega^2 p_I\theta\_c \Big) ,\\
c_3=& (\omega+\gamma)^2 \Big( (\frac{w_I}{w_S}\omega+\gamma)\gamma\theta\_w + \frac{w_I}{w_S} \omega^2 p_I\theta\_c \Big),\\
d_3=& \frac{(\omega+\gamma)}{\omega\gamma} \Big((\omega p_I+\gamma)\frac{w_I}{w_S}\phi\,+\,(\omega+\gamma)\gamma \Big)^2(\omega+\phi)^2. 
\end{align}

Note that $\phi\geq 0$, also $b_3$, $c_3$ and $d_3$ are all positive. However $a_3$ can be positive or negative.
If $a_3\geq 0$, $\partial\Delta/\partial\phi \geq 0$ for all feasible range of parameters, thus $\pro\Delta \leq 0$. 
If $a_3 < 0$, then the quadratic expression in the numerator of \eqref{eq:dd3dr} has a positive root, $\phi^*$, such that for $\phi>\phi^*$, $\partial\Delta/\partial\phi < 0$. An example of this scenario occures when $\theta\_w=0$ and $\theta\_c=1$, which is illustraited in the top-right panel of the Fig.\,\ref{pan2} panel (b). This is when the strength of isolation for awaiting people is the least, but the most for the confirmed cases. In this case 
\begin{equation}
\label{ineq:a3}
a_3 <0\iff\omega+\gamma<(\omega\,p_I+\gamma)\frac{w_I}{w_S}.
\end{equation}
Given that $\frac{w_I}{w_S}\geq 1$, and $0\leq\,p_I\leq\,1$, this inequality is hold when a perfect sensitive test is used, i.e., $p_I=1$, and a targeted tesing strategy is followed, i.e., $\frac{w_I}{w_S}>1$. \ali{i)what is the interpretation of this? 2) (Ben:) calculate the corresponding eigenvector to $\Rnum$, scale it to 1, and plot the population of each infected compartment, what does this tell us? }

>>>>

The Disease-Free Equilibrium (DFE) for the SIR model, Eqs. \eqref{model}, is found by setting the infected compartments to 0 and solving for the unknowns. The DFE is
\begin{equation}
\label{dfe}
S\_n^*= \frac{\rho}{\omega}\,N_0, \ S\_u^*= \frac{\omega-\rho}{\omega}\,N_0, \text{~and~} I_j=R_j=0 \ \text{for all }j.
\end{equation}
The corresponding \percap testing rate (Eq. \ref{F}) for the infected compartment $I$ at DFE is one of the key analysis parameters and can be simplified as 
\begin{equation}
\label{eq:fi}
\hat F_I = (\omega\rho/(\omega-\rho))w_I/w_S.
\end{equation}

@@

where parameters are specified in Table \ref{tab:params}. The next generation matrix for this model is $G = F V^{-1}$, where matrix $F$ represents the inflow of new infection to the infected compartments and matrix $V$ represents the flow in the infected compartments when the population is totally susceptible. 
Matrices $F$ and $V$ are
\begin{align}
\label{FV}
F =& \beta/N_0 \left[ \begin {array}{cccc} 
S\_u^* & (1-\theta\_w)\,S\_u^* & (1-\theta\_w)\,S\_u^* & (1-\theta\_c)\,S\_u^*\\
(1-\theta\_w)S\_n^* & (1-\theta\_w)^2\,S\_n^* & (1-\theta\_w)^2\,S\_n^* & (1-\theta\_w)(1-\theta\_c)\,S\_n^* \\ 
0&0&0&0\\
0&0&0&0
 \end {array} \right] \\
 =&\beta/N_0 \left[ \begin {array}{c} S\_u^* \\ (1-\theta\_w)S\_n^* \\ 0 \\ 0 \end {array} \right]
        \left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right], \text{and}\\  V=&
 \left[ \begin {array}{cccc}  
\hat F_I+\gamma&-\omega&0&0\\
-(1-p_I)\hat F_I&\omega+\gamma&0&0\\
-p_I \hat F_I&0&\omega+\gamma&0\\
0&0&-\omega&\gamma
\end {array} \right].
\end{align}
The matrix inverse of $V$ is 
\begin{align}
\label{vinv}
V^{-1} =&
\frac{1}{\gamma C}
\left[ \begin {array}{cccc}
\gamma(\omega+\gamma)^2 & \gamma\omega(\omega+\gamma)&0&0\\ \noalign{\medskip}
\gamma(\omega+\gamma)(1-p_I) \hat F_I & \gamma(\omega+\gamma)(\hat F_I+\gamma)&0&0 \\ \noalign{\medskip}
\gamma(\omega+\gamma) p_I \hat F_I & \gamma\omega p_I \hat F_I & C \gamma/(\omega+\gamma) & 0 \\ \noalign{\medskip}
\omega(\omega+\gamma) p_I \hat F_I & \omega^2 p_I \hat F_I & C \omega/(\omega+\gamma) & C
\end {array} \right],
\end{align}
where $C= \big( \gamma(\omega+\gamma)+(\gamma+\omega p_I)\hat F_I \big) (\omega+\gamma)$ and $\hat F_I$ is the \percap testing rate for the infected people and represented in Eq.\,\eqref{eq:fi}. Note that all the columns of matrix $V^{-1}$ summ up to $1/\gamma$.

@@

This is to provide a mathematical materials to prove that $\pro \Delta$ can be positive or negative, with $\Delta$ defined in Eq.\,\eqref{eq:abc}, and thus $\pro \Rnum < 0$, where $\Rnum$ is the basic reproduction number, given in Eq.\,\eqref{R0}. We can rewrite matrix $G_{11}$ in \eqref{G11} in the following form to simplify the calculations.
\begin{equation}
\label{G112}
G_{11} = \frac{\beta}{\gamma \, C} 
% \left[ \begin {array}{c}  (\omega-\rho)/\omega \\ (1-\theta\_w)\rho/\omega  \end {array} \right]
\left[ \begin {array}{c}  S\_u^*/N_0 \\ (1-\theta\_w)\,S\_n^*/N_0  \end {array} \right]
\left[ \begin {array}{cccc} 
C-C_1, C-C_1-C_2\end {array} \right],
\end{equation}
where $C$ is the same as the one in Eq. \eqref{eq:abc}, i.e., 
$$C=(\omega+\gamma)(\gamma(\omega+\gamma)+(\omega\,p_I+\gamma)\,\hat F_I),$$
and $C_1$ and $C_2$ are 
\begin{align}
\label{eq:C12}
C_1 =& (\omega+\gamma)(\theta\_w \, \gamma+\theta\_c\, \omega\, p_I) \hat F_I,\\
C_2 =& (\omega+\gamma)\gamma^2\,\theta\_w+(\theta\_w-\theta\_c)\gamma\,\omega\,p_I\,\hat F_I,
\end{align}
where $\hat F_I$ is given in Eq.\,\eqref{eq:fi}.
Note that for analysis brevity, we let $N_0=1$, thus $S\_u^*$ and $S\_n^*$ are in the scale of 0 to 1.
$\Rnum$ is in the same form as in Eq. \eqref{R0}  
$$\Rnum= \frac{\beta}{\gamma} (1-\Delta),$$
where 
\begin{equation}
\label{eq:del4}
\Delta= \frac{1}{C}\big(C_1\,S\_u^*+((C_1+C_2)(1-\theta\_w)+C\,\theta\_w)\,S\_n^*\big).
\end{equation}

{\bf The first goal} is to explore how changes in isolation, $\theta\_w$ and $\theta\_c$, affects $\Rnum$. Mathematically we would like to verify the sign of $\pder[\Rnum]{\theta\_w}$ and $\pder[\Rnum]{\theta\_c}$. We start with simpliying $\Delta$ \eqref{eq:del4} by factoring $\theta\_w$ and $\theta\_c$ in Eq.\,\eqref{eq:del4}. Thus, $\Delta$ can be rewritten as
\begin{equation}
\label{eq:del4_theta}
\Delta= \frac{1}{C}\Big(
-D_1\,S\_n^*\,\boldsymbol {\theta\_w^2}+
\big(-\omega^2\,p_I\,\hat F_I\,S\_n^*\,\boldsymbol{\theta\_c}\,+\,D_2\,S\_n^*\,+\,\gamma\,\hat F_I(\omega+\gamma) \big)\boldsymbol{\theta\_w}+
(\omega+\gamma\,S\_u^*)\omega\,p_I\,\hat F_I\,\boldsymbol{\theta\_c}
\Big),
\end{equation}
where
\begin{align}
\label{eq:del4_d1d2}
D_1=& (\omega+\gamma)\gamma^2+(\omega+\gamma+\omega\,p_I)\gamma\,\hat F_I, \\
D_2=& (3\omega+2\gamma)\gamma^2+(\omega+\gamma+2\omega\,p_I)\gamma\,\hat F_I+(\gamma+p_I\,\hat F_I)\omega^2.
\end{align}
The scaled expression of $\Delta$, specifically $\Delta\,C$, in Eq.\,\eqref{eq:del4_theta} is linear in $\theta\_c$ with a positive coefficient given by 
$$(\gamma\,S\_u^*\,+\omega(1-\theta\_w\,S\_u^*))\omega\,p_I\,\hat F_I.$$
This results in increasing $\Delta$, thus decreasing $\Rnum$ with respect to $\theta\_c$, that is $\pder[\Rnum]{\theta\_c}\leq 0$. Note that $C$ is independant of $\theta\_c$ and $\theta\_w$.

With a similar logic, the expression of $\Delta\,C$ derived from Eq.\,\eqref{eq:del4_theta} is a concave-down quadratic equation in $\theta\_w$, given by
\begin{equation}
\label{eq:del4_thetaw}
-D_1\,S\_n^*\,\boldsymbol {\theta\_w^2}+
\big(-\omega^2\,p_I\,\hat F_I\,S\_n^*\,\boldsymbol{\theta\_c}\,+\,D_2\,S\_n^*\,+\,\gamma\,\hat F_I(\omega+\gamma) \big)\boldsymbol{\theta\_w}.
\end{equation}
We show that the feasible range of $\theta\_w$ lies btween 0 and the vertex of this parabola where the parabola is increasing in $\theta\_w$, and so does $\Delta$ which results in inferring $\pder[\Rnum]{\theta\_w}\leq 0$.
It is enough to show that partial derivative of the expression \eqref{eq:del4_thetaw} with respect to $\theta\_w$ at $\theta\_w=1$ is non-negative. It follows that
\begin{align}
\label{eq:d_del4_thetaw}
\pder[\Delta]{\theta\_w}\,C\bigg\rvert_{\theta\_w=1} =&
(D_2-2D_1-\omega^2\,p_I\,\hat F_I\,\theta\_c)\,S\_n^*+\gamma\,\hat F_I(\omega+\gamma) \\
=& (\gamma(\omega+\gamma)+\gamma\omega^2+(1-\theta\_c)\omega^2\,p_I\,\hat F_I )\,S\_n^*
+\gamma(\omega+\gamma)\,\hat F_I\,(1-S\_n^*),
\end{align}
which is a positive quantity, given that $\theta\_c$ and $S\_n^*$ vary between 0 and 1.

{\bf The second goal} is to explore how changes in \percap testing intensity $\rho$ affects $\Rnum$. Mathematically we would like to verify the sign of $\pder[\Rnum]{\rho}$, which specifically depends on $\pder[\Delta]{\rho}$. We use the derived expressions for $S\_u^*$ and $S\_n^*$, given by Eqs.\,\eqref{dfe}, in $\Delta$ \eqref{eq:del4_theta}. Also, we define $\phi = \hat F_S = \frac{\rho \omega}{\omega-\rho}$, to reparametrize $\rho$. This is mainly to avoid singularity in $\hat F_I$ \eqref{eq:fi}, when testing intensity $\rho$ is very close to the rate of test return $\omega$. Thus, $\rho$ is reparametrized as 
\begin{equation}
\label{eq:phi}
\rho=\frac{\omega \phi}{\omega+\phi}.
\end{equation}
This one-to-one monotonic reparametrization enables us to simplify the mathematical expressions and explore the simpler $\pder[\Delta]{\phi}$ instead of the complicated $\pder[\Delta]{\rho}$.
% with an equivalent but simplified $\Delta$ in Eq.\,\eqref{eq:abc} as
% \begin{equation}
% \label{eq:del3}
% \Delta= \frac{K_1\,\phi^2+K_2\,\phi}{K_3},
% \end{equation}
% where
% \begin{align}
% \label{eq:K}
% K_1=& \frac{w_I}{w_S}\Big(((1+p_I)\omega+\gamma)\gamma\theta\_w+\omega^2 p_I\theta\_c \Big), \\
% K_2=& (\omega+\gamma)\Big( (\frac{w_I}{w_S}\omega+\gamma)\gamma\theta\_w + \frac{w_I}{w_S} \omega^2 p_I\theta\_c \Big),\\
% K_3=& (\omega+\gamma) \Big((\omega p_I+\gamma)\frac{w_I}{w_S}\phi\,+\,(\omega+\gamma)\gamma \Big)(\omega+\phi).
% \end{align}
The derivative is
\begin{align}
\label{eq:dd3dr}
\partial\Delta/\partial\phi=& \frac{1}{d_3} (a_3\,\phi^2+b_3\,\phi+c_3),
\end{align}
where

\begin{multline}
\label{eq:a3}
a_3 = \frac{w_I}{w_S}
\Bigg(\Big(
( \theta_{{w}}{{\it p\_I}}^{2}-\theta_{{c}}{{\it p\_I}}^
{2}\theta_{{w}} ) {\omega}^{3} 
+ ( 2\,\theta_{{w}}{{\it p\_I
}}^{2}-\theta_{{c}}{{\it p\_I}}^{2}-{\it p\_I}\,{\theta_{{w}}}^{2}-
\theta_{{c}}{\it p\_I}\,\theta_{{w}}-{{\it p\_I}}^{2}{\theta_{{w}}}^{2
}+2\,\theta_{{w}}{\it p\_I} ) \gamma\,{\omega}^{2} \\
 + ( -2\,{ \it p\_I}\,{\theta_{{w}}}^{2}-\theta_{{c}}{\it p\_I}+3\,\theta_{{w}}{
\it p\_I}-{\theta_{{w}}}^{2}+\theta_{{w}} ) {\gamma}^{2}\omega 
 + ( \theta_{{w}}-{\theta_{{w}}}^{2} ) {\gamma}^{3} \Big) \frac{w_I}{w_S}
 + ( -\theta_{{c}}{\it p\_I}\,\theta_{{w}}+\theta_{{c}}{\it p\_I}
 ) \gamma\,{\omega}^{2}+ \\
 ( \theta_{{w}}+\theta_{{c}}{\it
p\_I}-{\theta_{{w}}}^{2}-\theta_{{c}}{\it p\_I}\,\theta_{{w}} )
{\gamma}^{2}\omega+ ( \theta_{{w}}-{\theta_{{w}}}^{2} ) {
\gamma}^{3}
\Bigg),
\end{multline}
\begin{align}
\label{eq:abcd2}
b_3&= 2\frac{w_I}{w_S}(\omega+\gamma)\gamma\Big( 
(\omega+\gamma+\omega\,p_I)(2-\theta\_w)\,\gamma\,\theta\_w+ (1-\theta\_w)\,\omega^2 p_I\theta\_c+\omega^2 p_I\theta\_w 
\Big) ,\\
c_3&= (\omega+\gamma)^2\,\gamma\Big( 
(2-\theta\_w)\,\gamma^2\,\theta\_w+
(1+\frac{w_I}{w_S})\,\omega\,\gamma\,\theta\_w+
\frac{w_I}{w_S} \omega^2 p_I\theta\_c \Big),\\
d_3&= \frac{(\omega+\gamma)}{\omega} \Big((\omega p_I+\gamma)\frac{w_I}{w_S}\phi\,+\,(\omega+\gamma)\gamma \Big)^2(\omega+\phi)^2. 
\end{align}
Note that $\phi\geq 0$, also $b_3$, $c_3$ and $d_3$ are all positive. However $a_3$ can be positive or negative.
If $a_3\geq 0$, $\partial\Delta/\partial\phi \geq 0$ for all feasible range of parameters, thus $\pro\Rnum \leq 0$. 
If $a_3 < 0$, then the quadratic expression in the numerator of \eqref{eq:dd3dr} has a positive root, $\phi^*$, such that for $\phi>\phi^*$, $\partial\Delta/\partial\phi < 0$. An example of this scenario occures when $\theta\_w=0$ and $\theta\_c=1$, which is illustraited in the top-right panel of the Fig.\,\ref{pan2} panel (b). This is when the strength of isolation for awaiting people is the least, but the most for the confirmed cases. In this case 
\ali{I stoped here!}
\begin{equation}
\label{ineq:a3}
a_3 <0\iff\omega+\gamma<(\omega\,p_I+\gamma)\frac{w_I}{w_S}.
\end{equation}
Given that $\frac{w_I}{w_S}\geq 1$, and $0\leq\,p_I\leq\,1$, this inequality is hold when a perfect sensitive test is used, i.e., $p_I=1$, and a targeted tesing strategy is followed, i.e., $\frac{w_I}{w_S}>1$. \ali{i)what is the interpretation of this? 2) (Ben:) calculate the corresponding eigenvector to $\Rnum$, scale it to 1, and plot the population of each infected compartment, what does this tell us? }
